A Survey of Quantitative Descriptions of Molecular Structure

### 2012-07-05 paper.tex
Some minor updates. Added Bocatelli reference

\ctable[caption={A comparison of experimental versus calculated logP values
generated using the CDK, ACD Labs and ChemAxon software, for 10,000 molecules
taken from the proprietary logPstar dataset [REF?]},cap={},label={fig:logp},botcap,figure]
{c}
{}
{
  \includegraphics[width=\linewidth]{logp-comp-exptl}
}

>>>>

\ctable[caption={A comparison of experimental versus calculated logP values
generated using the CDK, ACD Labs and ChemAxon software, for 10,000 molecules
taken from the proprietary logPstar dataset.},cap={},label={fig:logp},botcap,figure]
{c}
{}
{
  \includegraphics[width=\linewidth]{logp-comp-exptl}
}
